---
title: "A3_BROOKE_HOLMES"
author: "Brooke Holmes"
output: html_document
---
Project Info
date: "January 26, 2022"
Brooke Holmes 20049015
GitHub Username: BrookeHolmes
https://github.com/BrookeHolmes/A3.git

Loading library and data
```{r}
library(dplyr)
df<-read.csv("InputData/FallopiaData.csv")
```

Removing rows with ‘Total’ biomass < 60
```{r}
df1<-filter(df,Total>=60)
df1
```
Reordering columns: ‘Total’, ‘Taxon’, ‘Senario’, ‘Nutrients’, and removing the others
```{r}
df2<-select(df1, Total, Taxon, Scenario, Nutrients)
df2
```

New column created: TotalG which is the Total converted to grams. TotalG replaced Total.
```{r}
df3 <- mutate(df2, TotalG=Total/1000)
df3 <- select(df3,TotalG, Taxon, Scenario, Nutrients)
```

Custom function that takes two inputs from the user: 
1. a vector of data to process
2. a string that defines what calculation to perform.
Average calculates the mean of the vector
Sum calculates the sum of the vector
Observation calculates the number of observed values in the vector
Any other command outputs an error
```{r}
func<-function(var1, var2){
  if(var2=="Average"){
    cat("The Average is: \n")
    avg <- mean(var1)
    return(avg)
  }
  if(var2=="Sum"){
    cat("The Sum is: \n")
    sum <- sum(var1)
    return(sum)
  }
  if(var2=="Observations"){
  cat("The Number of Observations are: \n")
  obs <- length(var1)
  return(obs)
  }
  return("Invalid Function Input")
}
```

Counting the total number of observations in the 'Taxon' column
```{r}
func(var1=df3$Taxon, var2="Observations")
```

Calculating the average TotalG for each of the two Nutrient concentrations
```{r}
print("Low Nutrients")
dfLow<-subset(df3, Nutrients=="low")
func(var1=dfLow$TotalG, var2="Average")

print("High Nutrients")
dfHigh<-subset(df3, Nutrients=="high")
func(var1=dfHigh$TotalG, var2="Average")
```

Writing the new data to a file called "WrangledData.csv" in the Output folder
```{r}
write.csv(df2, "Output/WrangledData.csv")
```
